---
title: "Publications"
output:
  distill::distill_article
links:
  - label: Google Scholar
    url: "https://scholar.google.com/citations?user=RSakTMYAAAAJ&hl=en"
  - label: ORCID iD
    url: "https://orcid.org/0000-0002-5455-2762"
  - label: ResearchGate
    url: "https://www.researchgate.net/profile/Maxine-Schaefer"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<center>
```{r, echo=FALSE}
# icon_link(
#     icon = "ai ai-google-scholar",
#     text = "Google Scholar",
#     url  = "https://scholar.google.com/citations?user=RSakTMYAAAAJ&hl=en"
# )
# icon_link(
#     icon = "ai ai-orcid",
#     text = "ORCID",
#     url  = "https://orcid.org/0000-0002-5455-2762"
# )
# icon_link(
#     icon = "ai ai-researchgate",
#     text = "Research Gate",
#     url  = "https://www.researchgate.net/profile/Maxine-Schaefer"
# )
```
</center>

# Journal Articles

**Schaefer, M.**, Probert, T., & Rees, S. (2020). The roles of phonological awareness, rapid automatised naming and morphological awareness in isiXhosa. Per Linguam, 36(1), 90–111. [https://doi.org/10.5785/36-1-878](https://doi.org/10.5785/36-1-878)

**Schaefer, M.**, & Kotzé, J. (2019). Early reading skills related to grade 1 english second language literacy in rural South African schools. South African Journal of Childhood Education, 9(1), a644. [https://doi.org/10.4102/sajce.v9i1.644](https://doi.org/10.4102/sajce.v9i1.644)

Bennett, W. G., **Diemer, M.**, Kerford, J., Probert, T., & Wesi, T. (2016). Setswana (South African). Journal of the International Phonetic Association, 46(2), 235–246. [https://doi.org/10.1017/S0025100316000050](https://doi.org/10.1017/S0025100316000050), [preprint version](https://sites.google.com/site/wmgbennett/papers)

**Diemer, M.**, van der Merwe, K., & de Vos, M. (2015). The development of phonological awareness literacy measures for isiXhosa. Southern African Linguistics and Applied Language Studies, 33(3), 325–341. [https://doi.org/10.2989/16073614.2015.1108769](https://doi.org/10.2989/16073614.2015.1108769), [preprint version](https://www.researchgate.net/publication/287797182_The_development_of_phonological_awareness_literacy_measures_for_isiXhosa)

# Reports

Jukes, M., Pretorius, E., **Schaefer, M.**, Tjasink, K., Roper, M., Bisgard, J., Mabhena, N. (2020). Setting Reading Benchmarks in South Africa. Department of Basic Education: Pretoria. [pdf](https://pdf.usaid.gov/pdf_docs/PA00X1NZ.pdf) 
